### 2011-02-15 Text/paper.tex
Small writeup is finished. Need to perform simulations with smaller grids.

@@

Here we present simulations for the domain of size $52\mathrm{x}52\mathrm{x}1500$ which simulates
the quarter of the channel using the mirror boundary conditions (Section \ref{append:sym}). That
results in the effective grid size as $100\mathrm{x}100\mathrm{x}1500$. The simulation is carried
out with the pressure gradient as:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d}x}=1.6\,10^{-6}.
\end{equation}
The initial film thickness was taken as $6$ nodes.

One can see the phase profile in the middle of the bubble in
Fig.\ref{fig:quarter:capillary:capillary01}. The associated capillary number is $0.053$ based on
the calculation of the bubble velocity in the center of the bubble. The radiuses in this simulation
are as $R_{axis}=0.93$ and $R_{diag}=1.06$. While $R_{axis}=0.93$ is underestimated parameter and
we can't take into the consideration apriori, one can consider parameter $R_{diag}=1.06$ the
parameters for the capillary number $0.053$ should be according to \citet{heil-threedim} as $0.97$
and $1.05$ according to the VOF simulations of \citet{wang-non-circular}. One can conclude that
even though the axis film thickness is not properly resolved the diagonal values are consistent and
can give an approximate information. 
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/quarter.eps}\\ %\hfill
\includegraphics[width=0.97\textwidth]{Figures/stream_cap01.eps}\\
\caption{Streamlines and phase profile of the quarter of the channel. The capillary number is
$0.053$ and the film thickness is underresolved. \label{fig:quarter:capillary:capillary01}}
\end{figure}
For underresolved schemes we performed a number of simulations on GPU code with the grid of size
$50\mathrm{x}50\mathrm{750}$. While changing the applied force in a manner indicated in Appendix
\ref{append:scaling} the velocity of the bubble was increased to obtain larger capillary numbers,
see Fig. \ref{fig:underresolved:capillaries}. One can see that the deviation between the diagonal
and axial radiuses are quite significant and they coincide only when the interface is resolved
($Ca\approx 1.0$). In calculations with better grids, i.e. quarter channels simulations on CPU, the
axial radius coincides with the diagonal in the $0.5\%$ range. Moreover, the capillary number curve
resembles already published date of \citet{heil-threedim} in a better way, see Fig.
\ref{fig:capillary:comparison}. 
\begin{figure}[ht]
\includegraphics[width=0.97\textwidth]{Figures/underresolved_capillaries.eps}
\caption{The underresolved profiles axis and diagonal radiuses versus capillary numbers. $50$
percent resolution starts from $Ca=1.0$, which is quite high. One can see it's exactly where
radiuses converge instead of $Ca=0.04$. {\color{red} To delete? However, one can see from
simulations Fig.
\ref{fig:wang:critical:capillary} and Fig.\ref{fig:thickness:variation:ca:ten} the thickness,
especially for Fig.\ref{fig:thickness:variation:ca:ten}, can significantly variate over a bubble
length.} \label{fig:underresolved:capillaries}}
\end{figure}

\section{Variation bubble length}
The works of \citet{heil-threedim} of \citet{wang-non-circular} show the variation of the bubble
thickness through the length of
bubble. The length variation is presented in Fig.\ref{fig:thickness:variation:ca:ten} and
Fig.\ref{fig:wang:bubble:shape}. While Fig. \ref{fig:wang:bubble:shape} indicates that the diagonal
radius has a variation for the rather small capillary numbers as $Ca<0.1$, another profile is
presented for the $Ca=10$ and shows the variation for the diagonal radius. We examined a bunch of
different capillaries numbers to present the diagonal radius variations over the length:
The axis and diagonal radiuses variation over the bubble are shown in Figure
\ref{fig:bubble:variation:capillaries}. The rather small capillary numbers one can see the increase
in the rear menisci of the diagonal radius which coincides with the results of
\citet{wang-non-circular}. One can see that variation over the length can be neglected
for relatively high $Ca$ numbers. 
\begin{figure}[ht]
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_36.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_46.eps}\\
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_61.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_88.eps}\\
\includegraphics[width=0.97\textwidth]{Figures/bubble_length_ca_one.eps}
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_117.eps}
\caption{The radiuses variations for the capillary number $Ca=0.46$.
One can see the diagonal radius different from the axial radius near the front of the tip which is
somehow coincides with the results of
\citet{heil-threedim}. The results are presented for the
capillary numbers (from left to right, top to bottom)
$0.36$,$0.46$, $0.61$, $0.88$,$1.06$,$1.17$. \label{fig:bubble:variation:capillaries}}
\end{figure}
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/variationoverlength.eps}
\caption{The variation of the bubble length for capillary number $Ca=10$. The x-axis scaled to
half-width of the microchannel height.  \label{fig:thickness:variation:ca:ten}}
\end{figure}

Concerning results indicated in Fig.
\ref{fig:thickness:variation:ca:ten} simulations are unstable that means one needs to work with
small surface tension ({\color{red} See results of Pagonabarraga}). One can see that the difference
between diagonal radius and
usual radius is of order of $4\%$. That means it's 2 percent of the channel height. If the
simulation is conducted by the grid $100\mathrm{x}100$ in the cross section that means that we will
see the difference in two grid nodes. Therefore the grid is $102\mathrm{x}102\mathrm{1500}$. It is
known from simulations that for the grid $102\mathrm{x}102\mathrm{x}1500$ the largest force gradient
is $2\mathrm{x}10^{-5}$ with free energy binary liquid parameters $A=0.04$,$k=0.04$ and $Ca\approx
1.0$. Therefore, we want to keep the same body force but to obtain larger capillary number. That
can be done through the scaling indicated in Appendix \ref{append:scaling}:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d}x}\propto \gamma Ca .
\end{equation}
Therefore the same body force can stand for capillary number ten times larger if the surface
tension is ten times smaller:
\begin{equation}
\gamma=\sqrt{\frac{8 k A}{9}}.
\end{equation}
The following can be satisfied if $A=0.004$ and $k=0.004$. Decreasing surface tension requires
increasing the mobility of the interface to be able to adjust to the interface
\cite{pagonabarraga-parameters}. We therefore performed the numerical simulation with those
parameters and $\Gamma=20$ for the interface to be stable. 
{\color{red} However, many authors state that increasing mobility kills
the
proper results of simulations}.
{\color{red} Need to wait results from bugaboo under LargeCap simulation}

\section{Capillary number}
We performed a number of simulations with quarter CPU code and GPU train simulations and compared
them with data obtained by \cite{heil-threedim}. After performing the simulations we determine the
$R_{axis}$, $R_{diag}$ versus calculated
capillary number
\begin{equation}
Ca=\frac{\mu_{liq} U_{bubble}}{\gamma}.
\end{equation}
To perform simulations we
started with the following parameters as
$k=0.04$,$A=0.04$,$\Gamma=1.0$. We performed different grids calculations with GPU and CPU codes.
The GPU code (see section \ref{section:bubble:train} about bubble train simulations) simulates a
quarter of the bubble and operates on the grid $100\mathrm{x}100\mathrm{x}1500$. The CPU refined
grid operates on whole $160\mathrm{x}160\mathrm{x}1500$. In this case we see short bubbles as the
length to height ratio is $\frac{500}{160}=3.125$. GPU  For GPU grids due to memory constrains we
chose the grid as $N_x\mathrm{x}N_y\mathrm{x}N_z=52\mathrm{x}52\mathrm{x}750$. One can see the
comparison presented in Fig. \ref{fig:capillary:comparison}.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/capillaries_comparison.eps}
\caption{The comparison between different runs of codes for the axial and the diagonal radiuses
versus capillary numbers. \ref{fig:capillary:comparison}}. One can see that the code mimics
behavior.
\end{figure}

One of the
profiles in
the middle of the bubble is shown in Fig. \ref{fig:steady:state:profile:example}.
\begin{table}
\begin{tabular}{|c|c|c|c|}
\hline
$N_{iter}$&$Ca$&$R_{axis}$&$R_{diag}$\\
$140000$&$0.0532$&$0.9379$&$1.075$\\
$150000$&$0.0533$&$0.9375$&$1.072$\\
$160000$&$0.0535$&$0.9372$&$1.069$\\
$170000$&$0.0536$&$0.9369$&$1.066$\\
$180000$&$0.0537$&$0.9366$&$1.062$\\
\hline
\end{tabular}
\caption{Results for the steady-state case. One can see that $200000$ steps are enough to structure
the bubble. However, the interface is underresolved. That could be the influence of the bubble
length.\label{table:steady:state}}
\end{table}
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/bullet.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/example_crossection.eps}\\
\caption{Slice in the middle of the bubble and
three-dimensional example. \label{fig:steady:state:profile:example}}
\end{figure}

To understand the influence of the steady-state case
For the steady-state regime the following parameters were obtained
We want to perform understanding of the steady state regime. As well probably it's good idea to
change domain as well, to reduce the length but to insure enough length of the bubble. The
steady-state calculations are performed on $52\mathrm{x}52\mathrm{x}750$ with large enough the
interface.

\section{Capillary number region}
The same as in the previous example can help us to identify the necessary capillary regime. The
most important thing is to establish different accentricity factors.

\section{Train simulation}
\label{section:bubble:train}
As far as the requirements for the grid are ``heavy'' we performed a bunch of simulations to
examine how the distance between bubbles influences on the thickness. For this purpose the
simulation was conducted on the grid 82x82x750. We examined different initialized distances between
bubbles. The initial lengths of bubbles were chosen as $300$, $350$, $400$, $450$, $500$, $550$
lattice units. Therefore, the corresponding initial distances between bubbles are
$450$,$400$,$350$,$300$,$250$ lattice units. On the steady state regime the distances become $386$,
$317$, $248$,$176$,$99$,$23$ lattice units. The corresponding capillary numbers calculated based on
the center bubble velocity are as follows $0.905$, $0.986$,$1.08$,$1.19$, $1.33$, $1.49$. The
calculated radiuses (diagonal radius equal to the axes radius) are as follows
$0.783$,$0.778$,$0.772$,$0.764$,$0.753$,$0.747$. Thus, one can see the great impact of the bubbles
on each other velocity for the given body force. However, in terms of the film thicknesses those
numbers look adequate. One can see the film thicknesses dependency on the capillary number for
simulations obtained by \citet{heil-threedim} and bubble train simulations data in Fig.
\ref{fig:capillaries:train}. One can see that the results are consistent and in a good agreement.
Therefore, though the bubble train mutual motion influences on the film thickness by increasing the
associated capillary number,  however, the film thickness is in accordance with the capillary
number correlation. Thus, the decrease of the numerical domain is quantified and can be used to
obtain the data. However, one should be cautious about the initialization, because the Poiseuille
flow initialization is deviated even further due to mutual motion of bubbles.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/capillaries_comparison_train.eps}
\caption{The comparison for the film thickness between \citet{heil-threedim} data and bubble train
simulations. Though, one can see that the decrease of the distance between bubbles causes the
increase in the associated capillary number, however, the correlation dependance between film
thickness and capillary number stays the same. This can help for simulations to reduce the
numerical domain. \label{fig:capillaries:train}}
\end{figure}

\section{Simulation setup}

\appendix{Symmetric boundary conditions}
\label{append:sym}
For the memory save we performed the simulation of the quarter of the channel while using the
antisymmetric boundary conditions. In the macroscopic variables the mirror boundary conditions
require to have the same scalar fields, but for velocity only tangential velocities are the same
but perpendicular have the opposite directions. This implies the following in terms of the
macroscopic variables:
\begin{equation}
\rho_B = \rho_F, \quad \phi_B = \phi_F \quad U_{B\tau}=U_{F\tau}, U_{B n}=U_{F n}, 
\end{equation}
 where $B$ and $F$ stand for the boundary and the nearest fluid node, respectively.

@@

\appendix{Scaling procedure}
\label{append:scaling}
For scaling purposes one need to obtain setup a body force as $\frac{\mathrm{d}P}{\mathrm{d}x}$. If
one obtained a certain velocity of the bubble with the associated gradient then another gradient
can be obtained through the porpotionality condition as:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d}x}=\frac{8}{N_y^2} \gamma Ca,
\end{equation}
or in other words th functionality can be extended as:
\begin{equation}
\dfrac{\dfrac{\mathrm{d}P_1}{\mathrm{d}x}}{\dfrac{\mathrm{d}P_2}{\mathrm{d}x}}=\frac{Ca_1}{Ca_2}
\frac{N_{
y2}^2 }{N_{y1}^2}
\end{equation}

>>>>

As well we performed longer simulations in the range of moderate capillary numbers after
$140000$, $160000$, $180000$, $200000$, $220000$, $240000$. The results for the capillary number
based on the bubble velocity in the middle crossection are shown in Table \ref{table:steady:state}. 
%{\color{red} What is it One of the
%profiles in
%the middle of the bubble is shown in Fig. \ref{fig:steady:state:profile:example}. }
\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
$N_{iter}$&$Ca$&$R_{axis}$&$R_{diag}$\\
$140000$&$0.0532$&$0.9379$&$1.075$\\
$150000$&$0.0533$&$0.9375$&$1.072$\\
$160000$&$0.0535$&$0.9372$&$1.069$\\
$170000$&$0.0536$&$0.9369$&$1.066$\\
$180000$&$0.0537$&$0.9366$&$1.062$\\
\hline
\end{tabular}\\
\begin{tabular}{|c|c|c|c|}
\hline
$N_{iter}$&$Ca$&$R_{axis}$&$R_{diag}$\\
$140000$&$0.3578$&$0.8657$&$0.8708$\\
$160000$&$0.3590$&$0.8650$&$0.8702$\\
$180000$&$0.3598$&$0.8647$&$0.8700$\\
$200000$&$0.3603$&$0.8645$&$0.8698$\\
$220000$&$0.3607$&$0.8644$&$0.8697$\\
$240000$&$0.3609$&$0.8645$&$ 0.8697$\\
\hline
\end{tabular}
\end{center}
\caption{Underresolved capillary number results and resolved Results for the steady-state case. One
can see that $200000$ steps are enough to structure
the bubble. \label{table:steady:state}}
\end{table}

%\begin{figure}
%\includegraphics[width=0.47\textwidth]{Figures/bullet.eps}\hfill
%\includegraphics[width=0.47\textwidth]{Figures/example_crossection.eps}\\
%\caption{Slice in the middle of the bubble and
%three-dimensional example. \label{fig:steady:state:profile:example}}
%\end{figure}

@@

Here we present simulations for the domain of size $52\mathrm{x}52\mathrm{x}1500$ which simulates
the quarter of the channel using the mirror boundary conditions (See Appendix \ref{append:sym}).
That
results in the effective grid size as $100\mathrm{x}100\mathrm{x}1500$. The simulation is carried
out with the pressure gradient as:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d}x}=1.6\,10^{-6}.
\end{equation}
The initial film thickness was taken as $6$ nodes.

One can see the phase profile in the middle of the bubble in
Fig.\ref{fig:quarter:capillary:capillary01}. For comparison reason the axisymmetric phase profile
for $Ca=0.6$ is presented in Fig. \ref{fig:bubble:axisymmetric}. The associated capillary number is
$0.053$ based on
the calculation of the bubble velocity in the center of the bubble. The radiuses in this simulation
are as $R_{axis}=0.93$ and $R_{diag}=1.06$. While $R_{axis}=0.93$ is underestimated parameter and
we can't take into the consideration apriori, one can consider parameter $R_{diag}=1.06$ the
parameters for the capillary number $0.053$ should be according to \citet{heil-threedim} as $0.97$
and $1.05$ according to the VOF simulations of \citet{wang-non-circular}. One can conclude that
even though the axis film thickness is not properly resolved the diagonal values are consistent and
can give an approximate information. 
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/quarter.eps}\\ %\hfill
\includegraphics[width=0.97\textwidth]{Figures/stream_cap01.eps}\\
\caption{Streamlines and phase profile of the quarter of the channel. The capillary number is
$0.053$ and the film thickness is underresolved. \label{fig:quarter:capillary:capillary01}}
\end{figure}
\begin{figure}[ht]
\includegraphics[width=0.97\textwidth]{Figures/square.eps}
\caption{The middle bubble phase profile. One can see that the diagonal radius coincides with the
axial radius. {\color{red} $Ca=0.5$} \label{fig:bubble:axisymmetric}}
\end{figure}

For underresolved schemes we performed a number of simulations on a GPU code with the grid of size
$50\mathrm{x}50\mathrm{750}$. While changing the applied force in a manner indicated in Appendix
\ref{append:scaling} the velocity of the bubble was increased to obtain larger capillary numbers,
see Fig. \ref{fig:underresolved:capillaries}. One can see that the deviation between the diagonal
and axial radiuses are quite significant and they coincide only when the interface is resolved
($Ca\approx 1.0$). In calculations with better grids, i.e. quarter channels simulations on CPU, the
axial radius coincides with the diagonal in the $0.5\%$ range. Moreover, the capillary number curve
resembles already published date of \citet{heil-threedim} in a better way, see Fig.
\ref{fig:capillary:comparison}. 
\begin{figure}[ht]
\includegraphics[width=0.97\textwidth]{Figures/underresolved_capillaries.eps}
\caption{The underresolved profiles axis and diagonal radiuses versus capillary numbers. $50$
percent resolution starts from $Ca=1.0$, which is quite high. One can see it's exactly where
radiuses converge instead of $Ca=0.04$. {\color{red} To delete? However, one can see from
simulations Fig.
\ref{fig:wang:critical:capillary} and Fig.\ref{fig:thickness:variation:ca:ten} the thickness,
especially for Fig.\ref{fig:thickness:variation:ca:ten}, can significantly variate over a bubble
length.} \label{fig:underresolved:capillaries}}
\end{figure}

\section{Velocity pattern}
We examined two different velocity patterns to identify change of pattern. Two capillaries numbers
were taken below and above the numbers indicated in Table \ref{table:recirculation:data}, as
$Ca=0.36$ and $Ca=0.88$.Velocity streamlines are
indicated in Fig. \ref{fig:streamlines:pattern}. One can see that the vortex indicated in
Fig.\ref{fig:heil:recirculating} doesn't appear in present calculations. This fact can be
explained because the simulation is carried our for the binary-liquid case but not free-surface
interface presented in the classical Bretherton problem. In the latter case the void phase pushes
the liquid towards the walls. In the present simulation there is no a void phase. Then the
streamlines have the ability to go through the interface and we exactly see this situation occuring.
\begin{figure}[ht]
\includegraphics[width=0.97\textwidth]{Figures/streamlines_ca036.eps}\\
\includegraphics[width=0.97\textwidth]{Figures/streamlines_ca088.eps}
\caption{Streamlines for $Ca=0.36$ and $Ca=0.88$. One can see that there are no vortexes created
before the bubble. It can be explained by the fact that the binary-liquid model is simulated
instead of free-surface interface gas air finger flow.\label{fig:streamlines:pattern}}
\end{figure}

\section{Variation bubble length}
The works of \citet{heil-threedim} of \citet{wang-non-circular} show the variation of the bubble
thickness through the length of
bubble. The length variation is presented in Fig.\ref{fig:thickness:variation:ca:ten} and
Fig.\ref{fig:wang:bubble:shape}. While Fig. \ref{fig:wang:bubble:shape} indicates that the diagonal
radius has a variation for the rather small capillary numbers as $Ca<0.1$, another profile is
presented for the $Ca=10$ and shows the variation for the diagonal radius. We examined a bunch of
different capillaries numbers to present the diagonal radius variations over the length:
The axis and diagonal radiuses variation over the bubble are shown in Figure
\ref{fig:bubble:variation:capillaries}. The rather small capillary numbers one can see the increase
in the rear menisci of the diagonal radius which coincides with the results of
\citet{wang-non-circular}. One can see that variation over the length can be neglected
for relatively high $Ca$ numbers. 
\begin{figure}[ht]
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_36.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_46.eps}\\
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_61.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_88.eps}\\
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_one.eps}
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_117.eps}
\caption{The radiuses variations for the capillary number $Ca=0.46$.
One can see the diagonal radius different from the axial radius near the front of the tip which is
somehow coincides with the results of
\citet{heil-threedim}. The results are presented for the
capillary numbers (from left to right, top to bottom)
$0.36$,$0.46$, $0.61$, $0.88$,$1.06$,$1.17$. \label{fig:bubble:variation:capillaries}}
\end{figure}
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/variationoverlength.eps}
\caption{The variation of the bubble length for capillary number $Ca=10$. The x-axis scaled to
half-width of the microchannel height.  \label{fig:thickness:variation:ca:ten}}
\end{figure}

Concerning results indicated in Fig.
\ref{fig:thickness:variation:ca:ten} simulations are unstable that means one needs to work with
small surface tension ({\color{red} See results of Pagonabarraga}). One can see that the difference
between diagonal radius and
usual radius is of order of $4\%$. That means it's 2 percent of the channel height. If the
simulation is conducted by the grid $100\mathrm{x}100$ in the cross section that means that we will
see the difference in two grid nodes. Therefore the grid is $102\mathrm{x}102\mathrm{1500}$. It is
known from simulations that for the grid $102\mathrm{x}102\mathrm{x}1500$ the largest force gradient
is $2\mathrm{x}10^{-5}$ with free energy binary liquid parameters $A=0.04$,$k=0.04$ and $Ca\approx
1.0$. Therefore, we want to keep the same body force but to obtain larger capillary number. That
can be done through the scaling indicated in Appendix \ref{append:scaling}:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d}x}\propto \gamma Ca .
\end{equation}
Therefore the same body force can stand for capillary number ten times larger if the surface
tension is ten times smaller:
\begin{equation}
\gamma=\sqrt{\frac{8 k A}{9}}.
\end{equation}
The following can be satisfied if $A=0.004$ and $k=0.004$. Decreasing surface tension requires
increasing the mobility of the interface to be able to adjust to the interface
\cite{pagonabarraga-parameters}. We therefore performed the numerical simulation with those
parameters and $\Gamma=20$ for the interface to be stable. 
{\color{red} However, many authors state that increasing mobility kills
the
proper results of simulations}.
{\color{red} Need to wait results from bugaboo.westgrid.ca under LargeCap simulation}

\section{Capillary number}
We performed a number of simulations with quarter CPU code and GPU train simulations and compared
them with data obtained by \cite{heil-threedim}. After performing the simulations we determine the
$R_{axis}$, $R_{diag}$ versus calculated
capillary number
\begin{equation}
Ca=\frac{\mu_{liq} U_{bubble}}{\gamma}.
\end{equation}
To perform simulations we
started with the following parameters as
$k=0.04$,$A=0.04$,$\Gamma=1.0$. We performed different grids calculations with GPU and CPU codes.
The GPU code (see section \ref{section:bubble:train} about bubble train simulations) simulates a
quarter of the bubble and operates on the grid $100\mathrm{x}100\mathrm{x}1500$. The CPU refined
grid operates on whole $160\mathrm{x}160\mathrm{x}1500$. In this case we see short bubbles as the
length to height ratio is $\frac{500}{160}=3.125$. GPU  For GPU grids due to memory constrains we
chose the grid as $N_x\mathrm{x}N_y\mathrm{x}N_z=52\mathrm{x}52\mathrm{x}750$. One can see the
comparison presented in Fig. \ref{fig:capillary:comparison}.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/capillaries_comparison.eps}
\caption{The comparison between different runs of codes for the axial and the diagonal radiuses
versus capillary numbers. \label{fig:capillary:comparison}}. One can see that the code mimics
behavior of the earlier published results.
\end{figure}

\section{Train simulation}
\label{section:bubble:train}
As far as the requirements for the grid are ``heavy'' we performed a bunch of simulations to
examine how the distance between bubbles influences on the thickness. For this purpose the
simulation was conducted on the grid 82x82x750. We examined different initialized distances between
bubbles. The initial lengths of bubbles were chosen as $300$, $350$, $400$, $450$, $500$, $550$
lattice units. Therefore, the corresponding initial distances between bubbles are
$450$,$400$,$350$,$300$,$250$ lattice units. On the steady state regime the distances become $386$,
$317$, $248$,$176$,$99$,$23$ lattice units. The corresponding capillary numbers calculated based on
the center bubble velocity are as follows $0.905$, $0.986$,$1.08$,$1.19$, $1.33$, $1.49$. The
calculated radiuses (diagonal radius equal to the axes radius) are as follows
$0.783$,$0.778$,$0.772$,$0.764$,$0.753$,$0.747$. Thus, one can see the great impact of the bubbles
on each other velocity for the given body force. However, in terms of the film thicknesses those
numbers look adequate. One can see the film thicknesses dependency on the capillary number for
simulations obtained by \citet{heil-threedim} and bubble train simulations data in Fig.
\ref{fig:capillaries:train} and in Fig. \ref{fig:capillary:comparison}. One can see that the
results are consistent and in a good agreement.
Therefore, though the bubble train mutual motion influences on the film thickness by increasing the
associated capillary number,  however, the film thickness is in accordance with the capillary
number correlation. Thus, the decrease of the numerical domain is quantified and can be used to
obtain the data. However, one should be cautious about the initialization, because the Poiseuille
flow initialization is deviated even further due to mutual motion of bubbles.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/capillaries_comparison_train.eps}
\caption{The comparison for the film thickness between \citet{heil-threedim} data and bubble train
simulations. Though, one can see that the decrease of the distance between bubbles causes the
increase in the associated capillary number, however, the correlation dependance between film
thickness and capillary number stays the same. This can help for simulations to reduce the
numerical domain. \label{fig:capillaries:train}}
\end{figure}

\section{Conclusion}
The present work conducts the binary-liquid simulations with the lattice Boltzman method. The
method is a continuous interface method. Along with similarity of results with already published
results of \citet{heil-threedim} and \citet{wang-non-circular}, the differencies were found,
especially in the velocity pattern. Results evedince that the lattice Boltzmann binary liquids
simulations can be used for simulation of gas bubbles in the microchannel.

\appendix
\section{Symmetric boundary conditions}
\label{append:sym}
For the memory save we performed the simulation of the quarter of the channel while using the
antisymmetric boundary conditions. In the macroscopic variables the mirror boundary conditions
require to have the same scalar fields, but for velocity only tangential velocities are the same
but perpendicular have the opposite directions. This implies the following in terms of the
macroscopic variables:
\begin{equation}
\rho_B = \rho_F, \quad \phi_B = \phi_F \quad U_{B\tau}=U_{F\tau}, U_{B n}=U_{F n}, 
\end{equation}
 where $B$ and $F$ stand for the boundary and the nearest fluid node, respectively.

@@

\section{Scaling procedure}
\label{append:scaling}
For scaling purposes one need to obtain setup a body force as $\frac{\mathrm{d}P}{\mathrm{d}x}$. If
one obtained a certain velocity of the bubble with the associated gradient then another gradient
can be obtained through the porpotionality condition as:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d}x}=\frac{8}{N_y^2} \gamma Ca,
\end{equation}
or in other words th functionality can be extended as:
\begin{equation}
\dfrac{\dfrac{\mathrm{d}P_1}{\mathrm{d}x}}{\dfrac{\mathrm{d}P_2}{\mathrm{d}x}}=\frac{Ca_1}{Ca_2}
\frac{N_{
y2}^2 }{N_{y1}^2}
\end{equation}
